---
title: "Day_3-6 Heart failure Data"
author: "Divyosmi Goswami"
date: "4/5/2021"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Welcome

**Hello Dear friends**
I welcome you to this Eda Notebook. This explores the heart faliure clinical data records dataset. it is gonna be fun. i hope you will enjoy using this notebook. this notebook is dedicated to my day 3-4 of my 100 days of code.

## Load Libraries
I will only need tidyverse for this time. Guess what I wil also need corrplot. 

```{r}
library(tidyverse)
library(corrplot) 
library()
```

## Data exploration

Let us dig up the data and explore it. Oh and yes 1 ***good news*** it is a totally cleaned data. Data set link (link)[https://archive.ics.uci.edu/ml/machine-learning-databases/00519/heart_failure_clinical_records_dataset.csv]



```{r}
x <- read.csv(url("https://archive.ics.uci.edu/ml/machine-learning-databases/00519/heart_failure_clinical_records_dataset.csv"))
x
```
```{r}
dim(x)
```
```{r}
summary(x)
```
```{r}
nrow(x)
```
```{r}
colnames(x)
```
```{r}
str(x)
```
## visualization
It is day 4 and I still have modelling to do. Hope to finish soon. Feel like writing hello world and telling see i did hello world. fun fact i never wrote hello world as the first program i remember writing 2+2 in python intepreter.
```{r}
vizCol = function (x){
    c = 1
    for(i in x){
    if(length(unique(i)) == 2){
        pie(table(i),main=colnames(x)[c])
    }
    else{
        hist(i,main= colnames(x)[c],xlab= colnames(x)[c])
    }
        c = c+1
    } 
}
vizCol(x)
```
```{r}
cor(x, method = c("pearson"))
corrplot(cor(x, method = c("pearson")))
cor(x, method = c("kendall"))
corrplot(cor(x, method = c("kendall")))
cor(x, method = c("spearman"))
corrplot(cor(x, method = c("spearman")))
```
I love experimenting and so does this interact function had thought about creating a better thing but vizCol already did that for me so it was interact-ive experiment time.

```{r}
interact = function (x){
    for(i in x){
        for(j in x){
            plot(i,j)
        }
    } 
}
interact(x)
```
#### Thank you for using.

